---
title: "Danielle Desrochers's CV"
author: Danielle Desrochers
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  sheet_is_publicly_readable:
    value: false
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true

---

```{css, echo=FALSE}
/* Turn-off side-bar for publications */
.pagedjs_page:not(:nth-of-type(-n+3)) {
  --sidebar-width: 0rem; /* Shrink sidebar width to 0 */
  --sidebar-background-color: #ffffff; /* Make colour same as background */
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")
googlesheets4::gs4_auth(email = "ddesrochers1212@gmail.com")


# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1roE5XSCE5NFfzHsBjb6rkWLZc7Lbv0hfRhymt603dRg/edit#gid=340636497",  
  pdf_mode = params$pdf_mode,
  sheet_is_publicly_readable = params$sheet_is_publicly_readable
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

<!-- ```{r} -->
<!-- # Build interactive network of positions coloured by section -->
<!-- # and connected if they occurred in the same year -->
<!-- datadrivencv::build_network_logo(CV$entries_data) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- if(params$pdf_mode){ -->
<!--   cat("View this CV online with links at _danielledesro.me/cv/_") -->
<!-- } else { -->
<!--   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](/desrochers_cv.pdf)") -->
<!-- } -->
<!-- ``` -->

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


Language Skills {#languageskills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```
```{r}
CV %>% print_skill_list()
```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------
This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](http://nickstrayer.me/datadrivencv/index.html).

Last updated on `r Sys.Date()`.


Main
================================================================================

Danielle Desrochers {#title}
--------------------------------------------------------------------------------
### Aquatic Biologist \| Data Scientist \| ADD TITLE

```{r}
CV %<>% print_text_block("intro") 
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

:::aside
## Awards
- Study in Italy Grant (2021)
- Indspire Building Better Futures Scholarship (2014-2021)
- Louis Riel Awards (2014-2016)
- Guertin Centennial Entrance Scholarship, U of M (2014)
- Cambrian Credit Union Learning for Life Award (2014)
- MASRC - 2002 NAIG Legacy Athlete Scholarship (2014) 
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
:::

```{r}
CV %<>% print_section('education')
```


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions_a')
```

\pagebreak
Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

:::aside
<!-- <span style="font-weight: 300; font-size: 1.1rem; color: #000">Research Skills</span> -->
<!-- <br> -->
## Research Skills
- Safely travel to sampling locations.<br>
- Comfortable working in remote outdoor locations, in demanding weather conditions and for extended periods of time.<br>
- Ability to record complete and accurate field notes.<br>
- Knowledgeable in field sampling techniques, laboratory anlyses, and environmental monitoring.<br>
- Effective data visualization.<br>
- Data analysis.<br>
- Statistical and mathematical modelling.
:::
```{r}
CV %<>% print_section('research_positions_b')
```

\pagebreak
Other Employment {data-icon=book}
--------------------------------------------------------------------------------
::: aside
##  Other {#other}

- Capable of working effectively and collaboratively with team members to maximize productivity and efficiency.
- Natural leader with great teamwork and problem-solving skills.
- A wealth of experience communicating to the general public, both in French and English.
:::
```{r}
CV %<>% print_section('other_employment')
```



\pagebreak
Publications, Posters, and Talks {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('data_science_writings')
```
